InteroceptionStudy_GPValidation

### 2022-12-03 Old scripts/IAPS_PREPROCESSING_2021.Rmd
test for Review
recover the power analyses files

tmp.df4$trigger2 <- tmp.df4$trigger

@@

unique(tmp.df4$trigger2)
unique(tmp.df4$trigger)
unique(tmp.df4$tNo)

# \why?
unique(tmp.df4$text)

tmp.df4<- tmp.df4%>%
  group_by(ssid, tNo, text)%>%
  mutate(stdev_gaze_x = sd(gaze_x_cor_pix, na.rm = TRUE))%>%
  mutate(stdev_gaze_y = sd(gaze_y_cor_pix, na.rm = TRUE))

@@

db_parsed$screencontent_no <- if_else(db_parsed$screencontent == 'fixation', 1,
                                      if_else(db_parsed$screencontent == 'stim', 2,
                                              if_else(db_parsed$screencontent == 'ValenceResp', 3,
                                                      if_else(db_parsed$screencontent == 'IntResp', 4, NULL))))

@@

# rm(tmp.df4_sum_fullt)
# testna<- subset(tmp.df4_sum_fullt, is.na(tmp.df4_sum_fullt$mean_fix_dur) == TRUE)
# 
# tmp.df4_sum_fullt

tmp.df4_sum_full
```

@@

db_beh2$triggeracq <- db_beh2$trigger
unique(db_beh2$ssid)

@@

# tmp.df4_sum_full<- tmp.df4_sum_full%>%
#   arrange(ssid, tNo, screencontent_no)

colnames(tmp.df4_sum_full)
```

@@

trigger<- db_leda2 %>%
  subset(ssid == 348)%>%
  select(order, Event.NID, trigger,Event.Nr)
```

@@

colnames(db_leda_bio)

db_leda_bio$BIO_Event.NID<- db_leda_bio$Event.NID
db_leda_bio$BIO_filename <- db_leda_bio$filename

@@

# unique(db_leda_bio$trigger)

# subset out rest period
db_leda_bio<- subset(db_leda_bio, Event.Nr>1)

db_leda_bio<- subset(db_leda_bio, CDA.nSCR!= "NaN")
range(db_leda_bio$Event.Nr)

# transform NaNs into proper NA
db_leda_bio[db_leda_bio == "NaN"] <- NA

# move counter to 1
range(db_leda_bio$Event.Nr-1)
# range(db_leda_bio$Event.Nr)
# trigger$Event.Nr<- NULL

db_leda_bio$order <- db_leda_bio$Event.Nr-1
# db_leda_bio$trigger<- NULL

# merge trigger
trigger$Event.NID<- NULL
trigger$ssid<- NULL
View(db_leda_bio)

db_leda_bio$order
# db_345_355$order

trigger<- db_345_355 %>%
  group_by(order,trigger, tNo)%>%
  summarise_at(c('ssid'), mean, na.rm = TRUE)
  # select(db_345_355, c(trigger, tNo, order))

  trigger$ssid<- NULL

  db_leda_bio<- left_join(db_leda_bio, trigger)

tmp.df4_sum_full

leda_bioames <- colnames(db_leda_bio)

leda_bioames
newnames<- c("Event.Nr", paste0("BIO_", paste(leda_bioames[2:16])),"BIO_Event.NID","BIO_filename"  ,"ssid","order","trigger")

newnames

db_leda_bio_backup<- db_leda_bio

colnames(db_leda_bio_backup)

names(db_leda_bio) <- newnames

colnames(db_leda_bio)

# db_leda_bio$ssid <- db_leda_bio$BIO_ssid

# db_leda_bio$BIO_ssid<-NULL

db_leda_bio

db_leda_bio$ssid<- as.character(db_leda_bio$ssid)

# db_leda_bio$order<- db_leda_bio$BIO_order

unique(tmp.df4_sum_full$Event.Nr)

db_leda_bio$BIO_Event.NID<- NULL
db_leda_bio$BIO_filename<- NULL

tmp.df4_sum_full_bio<- left_join(tmp.df4_sum_full,  db_leda_bio, by = c("ssid", "order"))

colnames(tmp.df4_sum_full_bio)

write_csv(db_leda_bio, "db_leda_bio_346_347_ledagsr.csv")

write_csv(db_leda_bio, "db_leda_bio_346_355_ledagsr.csv")
```

```{r eval=FALSE, include=FALSE}
# stim
db_leda_bio_stim<-subset(db_leda_bio, db_leda_bio$trigger< 100)
unique(db_leda_bio_stim$trigger)

@@

@@

# db_leda_bio_stim$trigger<- as.character(db_leda_bio_stim$trigger)

db_leda_bio$order<- db_leda_bio$Event.Nr

tmp.df4_sum_full_stim_gp_leda_beh_self$ssid<- as.character(tmp.df4_sum_full_stim_gp_leda_beh_self$ssid)

tmp.df4_sum_full_stim_gp_leda_beh_self$trigger<- as.character(tmp.df4_sum_full_stim_gp_leda_beh_self$trigger)

@@

cor(tmp.df4_sum_full_biot1$arousal, tmp.df4_sum_full_biot1$Global.Mean.y, use = 'complete.obs')

@@

import biopac heart rate
```{r}

nrow(tmp.df4_sum_full_bio)

# now read them
# old
db_biohr <-
  list.files(pattern = "*.xls", 
             full.names = T) %>% 
  map_df(~read_biohr(.))

db_biohr$Order<- NULL
db_biohr$filename<- NULL
db_biohr$trigger<- as.factor(as.character(db_biohr$trigger))

unique(db_biohr$ssid)

db_biohr$ssid<- as.factor(as.character(db_biohr$ssid))

#HR BIOPAC

```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/Data Collection 2019- 2020/2020/InteroStudyBIOPAC/IAPS/Processed/HR/345_355")
library(readxl)
library(dplyr)
# db_HR_bio <- read_excel("310_IAPS_Physio_HR.xls")

# db_HR_bio<- db_HR_bio[6:nrow(db_HR_bio),]

library(data.table)
library(purrr)
# import
read_biohr <- function(flnm) {
  read_excel(flnm) %>% 
    mutate(filename = flnm)
}

# now read them
db_HR_bionew <-
  list.files(pattern = "*.xls", 
             full.names = T) %>% 
  map_df(~read_biohr(.))

db_HR_bio<- db_HR_bionew

unique(db_HR_bionew$filename)
nrow(db_HR_bionew)

# test<- subset(db_HR_bio, db_HR_bio$filename == "./607_IAPS_Physio_HR.xls")

levels(as.factor(db_HR_bio$filename))

db_HR_bio$ssid<- substr(db_HR_bio $filename, 3,5)

db_HR_bio$filename<- NULL

# 
db_HR_bio$`Stim-Response Analysis`

# flag stimulus
db_HR_bio$stim <- if_else(grepl('Stimulus', (db_HR_bio$`Stim-Response Analysis`)) == TRUE, db_HR_bio$`Stim-Response Analysis`, NULL)

library(tidyr)

db_HR_bio<- db_HR_bio%>%
  group_by(ssid)%>%
  fill(stim)

db_HR_bio

levels(as.factor(db_HR_bio$ssid))

#  remove na in the mean heart rate

db_HR_bio<- subset(db_HR_bio, !is.na(db_HR_bio$...2))

db_HR_bio$mhrtext<- is.character(db_HR_bio$...2)

db_HR_bio<- subset(db_HR_bio, !grepl('interval ', db_HR_bio$`Stim-Response Analysis`) == TRUE)

# loosing participants here
View(db_HR_bio)

db_HR_bio<- subset(db_HR_bio, !grepl('Interval ', db_HR_bio$`Stim-Response Analysis`) == TRUE)

# test<- subset(db_HR_bio, grepl('Interval ', db_HR_bio$`Stim-Response Analysis`) == TRUE)
# levels(as.factor(db_HR_biotest$ssid))

db_HR_bio<- subset(db_HR_bio, !grepl('Time', db_HR_bio$`Stim-Response Analysis`) == TRUE)

#db_HR_biotest1<- subset(db_HR_biotest, !is.na(db_HR_biotest$stim))

#test<- subset(db_HR_bio, db_HR_bio$ssid == 607)

levels(as.factor(db_HR_bio$ssid))

db_HR_bio<- subset(db_HR_bio, !is.na(db_HR_bio$`Stim-Response Analysis`))

db_HR_bio$...3<- NULL
db_HR_bio$...4<- NULL

db_HR_bio<- subset(db_HR_bio, !is.na(db_HR_bio$...2))

db_HR_bio<- subset(db_HR_bio, db_HR_bio$...2 != 'Mean(CH 40)')
db_HR_bio$timestart<- db_HR_bio$`Stim-Response Analysis`

db_HR_bio$Mean_HR<- db_HR_bio$...2

db_HR_bio<- db_HR_bio%>%
  arrange((as.numeric(timestart)), ssid)

db_HR_bio<- subset(db_HR_bio, !is.na(db_HR_bio$stim))

db_HR_bio$trigger <- substr(db_HR_bio$stim, 10,13)

# for soem reason this 
unique((as.numeric(db_HR_bio$trigger)-128))

db_HR_bio$trigger_200<- if_else(db_HR_bio$trigger> 103, TRUE, FALSE)

db_HR_bio$trigger2 <- if_else(db_HR_bio$trigger_200 == TRUE, as.numeric(db_HR_bio$trigger)-128, as.numeric(db_HR_bio$trigger))

unique((as.numeric(db_HR_bio$trigger2)))

#subset(db_HR_bio, db_HR_bio$ssid!= 328)%>%
#  group_by(timestart, ssid)%>%
 # mutate(EventNR= 1:225)

# this will delete fixation and stuff so no
db_HR_bio1<- subset(db_HR_bio,db_HR_bio$trigger2> 15)

db_HR_bio1<- db_HR_bio%>%
  arrange(ssid, as.numeric(timestart))

db_HR_bio1<- subset(db_HR_bio1,!is.na(db_HR_bio1$stim))

#tno
#subset(db_HR_bio1, db_HR_bio1$ssid != 328)%>%
table(is.na(db_HR_bio1$ssid))
# 
# db_HR_bio1<- db_HR_bio1%>%
#   arrange(as.numeric(timestart), ssid)

# use this
table(db_HR_bio1$ssid!= 328)
db_HR_bio1no328<-subset(db_HR_bio1, db_HR_bio1$ssid!= 328)

db_HR_bio1no328$trigger2
db_HR_bio1no328<- subset(db_HR_bio1no328, trigger2> 15 & trigger2<106)

db_HR_bio1no328$trigger<- db_HR_bio1no328$tNo
# db_HR_bio1no328

# db_HR_bio1no328<- db_HR_bio1no328 %>%
#   arrange(ssid, trigger2)%>%
#   filter(!duplicated(trigger2))

View(trigger)
db_HR_bio1no328<- db_HR_bio1no328$t %>%
  group_by(ssid)%>%
  mutate(tNo =  -6:(n()-7)) #56 trials

unique(db_HR_bio1no328$tNo)

range(db_HR_bio1no328$tNo)

table(db_HR_bio1no328$tNo)

# test<- subset(db_HR_bio1no328, tNo>49)
# 
# db_HR_bio328<-subset(db_HR_bio1, db_HR_bio1$ssid== 352)
# 
# subset(db_HR_bio328, trigger> 15 & trigger<72)

db_HR_bio1no328<- db_HR_bio1no328%>%
  arrange(ssid,as.numeric(timestart))

```{r}
# db_HR_bio2<-

unique(db_HR_bio1no328$stim)
db_HR_bio1no328<- db_HR_bio1no328 %>%
  group_by(ssid)%>%
  mutate(tNo = -6:(n()-7))

unique(db_HR_bio1no328$tNo)
```

```{r}
View(db_HR_bio1no328)

unique(db_HR_bio1no328$ssid)
unique(db_HR_bio328$ssid)
# db_HR_bio2<- bind_rows(db_HR_bio1no328,db_HR_bio328)
db_HR_bio2<-db_HR_bio1no328

colnames(db_HR_bio2)

levels(as.factor(db_HR_bio1no328$ssid))
# db_HR_bio2$ssid<-db_HR_bio2$`as.numeric(ssid)`

#mereg old and new heart rate
# now read them
# db_biohr$trigger
# 
# db_biohr$tno<-db_biohr$trigger
# db_HR_bio2$trigger
# colnames(db_biohr)
# 
# colnames(db_HR_bio2)
# 
# db_biohr$Mean_HR<- db_biohr$HR_BIO
# 
# db_biohr$timestart<- db_biohr$Time
# 
# 
# left_join(db_HR_bio2, db_biohr)

colnames(db_HR_bio2)
db_HR_bio2<- select(db_HR_bio2, c(timestart,Mean_HR, tNo, ssid,trigger2,trigger_200, trigger,stim,mhrtext))

# store only fixation screens

# create screecontr.treatment()
unique(db_HR_bio2$trigger)
unique(db_HR_bio2$trigger2)

db_HR_bio2$screen_content<- if_else(db_HR_bio2$trigger == 100, "Rest",
                                    if_else(db_HR_bio2$trigger == 101, "fixation",
                                    if_else(db_HR_bio2$trigger == 102, "valence",
                                    if_else(db_HR_bio2$trigger == 103, "arousal",
                                    "stim"))))

unique(db_HR_bio2$trigger)

db_HR_bio2$timestart<- as.numeric(db_HR_bio2$timestart)
db_HR_bio2.1<- db_HR_bio2 %>%
  group_by(ssid)%>%
  arrange(ssid, timestart)%>%
  group_by(ssid,screen_content)%>%
  # arrange(ssid, timestart)%>%
  mutate(tNo =  1:n())
   arrange(timestart,ssid)
  # subset(trigger == 100)

unique(db_HR_bio2.1$tNo)

unique(db_HR_bio2.1$tNo-8)
table(db_HR_bio2.1$tNo)

db_HR_bio2.1$tNo2<- if_else(db_HR_bio2.1$screen_content == "Rest", -7,
                           as.numeric(as.character(db_HR_bio2.1$tNo)))

db_HR_bio2.1$tNo3<- if_else(db_HR_bio2.1$tNo2 >0 &  db_HR_bio2.1$tNo2< 7, db_HR_bio2.1$tNo2-7,
                          if_else(db_HR_bio2.1$tNo2  >6, db_HR_bio2.1$tNo2-6, db_HR_bio2.1$tNo2))

table(db_HR_bio2.1$tNo3)
test352<- subset(db_HR_bio2.1, ssid == 352)
test353<- subset(db_HR_bio2.1, ssid == 353)
table(test352$tNo3)

write_csv(test352, "test352.csv")

# fixed the issue was trial 15 is supposed to be trigger 23 but we also had a 70, that can be seen on the psychopy data files
write_csv(test353, "test353.csv")

# on 353 the issue was a 99 trigger bveing loaded as a stim

# export 352 and 353 and corect manually, they seems ot have an extra trigger

db_352 <- read_csv("352_Biohr_fixed.csv")
db_353 <- read_csv("353_Biohr_fixed.csv")
unique(db_352$ssid)
db_352
nrow(db_353)

# new dataset withouth the problem ssids
db_HR_bio2.2<- subset(db_HR_bio2.1, ssid != "352")
db_HR_bio2.2<- subset(db_HR_bio2.2, ssid != "353")

nrow(db_HR_bio2.2)

unique(db_HR_bio2.2$ssid)

db_352_353<- bind_rows(db_352, db_353)

nrow(db_352_353)

db_HR_bio2.2$ssid<- as.character(db_HR_bio2.2$ssid)
db_352_353$ssid<- as.character(db_352_353$ssid)

db_352_353$trigger <- as.character(db_352_353$trigger)

nrow(db_HR_bio2.2)
# nrow(db_HR_bio2.1) 2021 result should be less than this

nrow(db_352_353)

db_HR_bio2.3<- bind_rows(db_HR_bio2.2,db_352_353)
nrow(db_HR_bio2.3)
# order

db_HR_bio2.3.1<- db_HR_bio2.3 %>%
  group_by(ssid)%>%
  arrange(ssid, timestart) %>%
  group_by(ssid,screen_content)%>%
  # arrange(ssid, timestart)%>%
  mutate(tNo =  1:n())
   # arrange(timestart,ssid)
  # subset(ssid == 353)

table(db_HR_bio2.3.1$tNo)

# test<- subset(db_HR_bio2.3.1, ssid == "353")

unique(db_HR_bio2.3.1$tNo)

db_HR_bio2.3.1$tNo2<- if_else(db_HR_bio2.3.1$screen_content == "Rest", -7,
                           as.numeric(as.character(db_HR_bio2.3.1$tNo)))

db_HR_bio2.3.1$tNo3<- if_else(db_HR_bio2.3.1$tNo2 >0 &  db_HR_bio2.3.1$tNo2< 7, db_HR_bio2.3.1$tNo2-7,
                          if_else(db_HR_bio2.3.1$tNo2  >6, db_HR_bio2.3.1$tNo2-6, db_HR_bio2.3.1$tNo2))

unique(db_HR_bio2.3.1$tNo3)
```

```{r}
unique(db_HR_bio2.3.1$screen_content)
table(is.na(db_HR_bio2.3.1$screen_content))

str((db_HR_bio2.3.1))
# str(db_biohrold2)
db_biohr$tNo<- db_biohr$tno
db_biohrold2<- db_biohr

db_biohrold2<- select(db_biohr, c(timestart,Mean_HR, tNo, ssid))
unique(db_biohrold2$tNo)

db_HR_bio2$timestart<- as.numeric(db_HR_bio2$timestart)

View(db_biohrold2)
db_biohrold2$timestart<- as.numeric(db_biohrold2$timestart)

# View(db_HR_bio2)
db_HR_bio2$Mean_HR<- as.numeric(db_HR_bio2$Mean_HR)
# db_biohrold2$Mean_HR<- as.numeric(db_biohrold2$Mean_HR)

db_HR_bio2$tNo<- as.character(db_HR_bio2$tNo)

db_biohrold2$tNo<- as.character(db_biohrold2$tNo)
db_HR_bio2$ssid<- as.character(db_HR_bio2$ssid)

db_biohrold2$ssid<- as.character(db_biohrold2$ssid)

str(db_HR_bio2)

# db_biohrold2test<- subset(db_biohrold2, db_biohrold2$tNo != 100)
# db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 101)
# db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 102)
# db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 103)
# db_HR_bio2$subj<- as.factor(db_HR_bio2$ssid)
# db_biohrold2test$subj<- as.factor(db_biohrold2test$ssid)
# db_biohrold2test$ssid<- NULL
# db_HR_bio2$ssid<- NULL

str(db_HR_bio2)

db_HR_bio2<- db_HR_bio2[,1:4]
db_HR_bio2$Mean_HR<- as.numeric(db_HR_bio2$Mean_HR)

db_biohrold2test$Mean_HR<- as.numeric(db_biohrold2test$Mean_HR)

db_HR_bio2$timestart<- as.numeric(db_HR_bio2$timestart)

db_biohrold2test$timestart<- as.numeric(db_biohrold2test$timestart)

# final
colnames(db_HR_bio_final)
db_HR_bio2.3.1
colnames(db_HR_bio2.3.1)

unique(db_HR_bio2.3.1$tNo)
db_HR_bio2.3.1
# db_HR_bio2.3.2<-select()
db_HR_bio_final<- select(db_HR_bio2.3.1, c(1:12))

table(is.na(db_HR_bio_final$Mean_HR))

# db_HR_bio_final<- bind_rows(db_HR_bio2, db_biohrold2test)

View(db_HR_bio_final)

# db_HR_bio_final$ssid<- db_HR_bio_final$subj
levels(as.factor(db_HR_bio_final$ssid))

db_HR_bio_final$subj<- NULL

write_csv(db_HR_bio_final, 'db_HR_bio_final_mar5.csv')

write_csv(db_HR_bio_final, 'db_HR_bio_final_346_355_withfix.csv')

db_HR_bio_final$tNo

db_HR_bio_final$tNo

db_HR_bio1$tNo<- -6:49

db_HR_bio_final$tNo<- if_else(as.numeric(db_HR_bio_final$tNo) < 0, as.numeric(db_HR_bio_final$tNo), as.numeric(db_HR_bio_final$tNo)+1)

db_HR_bio_final$BIO

merge heart rate

```{r}
tmp.df4_sum_full_bio$ssid<- as.character(tmp.df4_sum_full_bio$ssid)
db_HR_bio_final$ssid<- as.character(db_HR_bio_final$ssid)

colnames(tmp.df4_sum_full_bio)

unique(tmp.df4_sum_full_bio$tNo)
tmp.df4_sum_full_bio$tNo3<- tmp.df4_sum_full_bio$tNo
tmp.df4_sum_full_bio1<- tmp.df4_sum_full_bio
tmp.df4_sum_full_bio1$tNo<-NULL

unique(tmp.df4_sum_full_bio$screencontent)
unique(db_HR_bio_final$screen_content)

unique(tmp.df4_sum_full_bio$screen_content)

tmp.df4_sum_full_bio$screen_content<- if_else(tmp.df4_sum_full_bio$screencontent == "ValenceResp", "valence",
                                              if_else(tmp.df4_sum_full_bio$screencontent == "IntResp", "arousal", tmp.df4_sum_full_bio$screencontent))

db_HR_bio_final

table(is.na(tmp.df4_sum_full_bio_hr$Mean_HR))

test<- subset(tmp.df4_sum_full_bio_hr, is.na(Mean_HR))

db_HR_bio_final_norest<- subset(db_HR_bio_final, screen_content!= "Rest")

unique(tmp.df4_sum_full_bio$tNo)

unique(db_HR_bio_final_norest$tNo)

# remeber to do this otherwise tno will be matchjing wrong data
db_HR_bio_final_norest$tNo<- db_HR_bio_final_norest$tNo3

tmp.df4_sum_full_bio_hr <- left_join(tmp.df4_sum_full_bio, db_HR_bio_final_norest, by = c('ssid', 'tNo', 'screen_content'))

unique(tmp.df4_sum_full_bio_hr$tNo)

table(is.na(tmp.df4_sum_full_bio_hr$Mean_HR))

Merge self reports

# add the self report
```{r}

View(tmp.df4_sum_full_bio_hr)

library(readxl)
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport")

View(db_selfrep)
db_selfrep <- read_excel("db_self_rep_345_356_final.xlsx")

db_selfrep$ssid <- as.character(db_selfrep$`Participant No`)

tmp.df4_sum_full_bio_hr$ssid <- as.character(tmp.df4_sum_full_bio_hr$ssid)

unique(tmp.df4_sum_full_bio_hr_self$ssid)
table(is.na(tmp.df4_sum_full_bio_hr$Mean_HR))

tmp.df4_sum_full_bio_hr_self <- left_join(tmp.df4_sum_full_bio_hr, db_selfrep, by = 'ssid')
table(is.na(tmp.df4_sum_full_bio_hr_self$Mean_HR))
write_csv(tmp.df4_sum_full, 'tmp.df4_sum_full_bio_hr_self_345_356.csv')

merge parsed data
```{r}
tmp.df4_sum_full_bio_hr_self
db_parsed_summarised2$ssid<- as.character(db_parsed_summarised2$ssid)

tmp.df4_sum_full_bio_hr_self_parsed <- left_join(tmp.df4_sum_full_bio_hr_self, db_parsed_summarised2, 
                             by = c("ssid", "trialUnq", "tNo", "screencontent"))

# tmp.df4_sum_full<- left_join(tmp.df4_sum,db_parsed_summarised2, by = c("ssid", "trialUnq", "tNo", "screencontent"))

# save the timecourse data and the aggregated data

tmp.df4_sum_full_bio_hr_self_parsed

# merge behavioural data
db_beh3$ssid<- as.character(db_beh3$ssid)
db_beh3$tNo <- as.character(db_beh3$tNo)
tmp.df4_sum_full_bio_hr_self_parsed$tNo<- as.character(tmp.df4_sum_full_bio_hr_self_parsed$tNo)
# tmp.df4_sum_full<-

tmp.df4_sum_full_bio_hr_self_parsed
table(is.na(tmp.df4_sum_full_bio_hr_self_parsed$Mean_HR))

tmp.df4_sum_full_bio_hr_self_parsed<- left_join(tmp.df4_sum_full_bio_hr_self_parsed, db_beh3, by = c('ssid', 'tNo'))

View(db_beh3)
tmp.df4_sum_full<- tmp.df4_sum_full%>%
  arrange(ssid, tNo, time)

tmp.df4_sum_full_bio_hr_self_parsed$screencontent_no

tmp.df4_sum_full_bio_hr_self_parsed$TAS
# tmp.df4_sum_full_bio_hr_self_parsed<- tmp.df4_sum_full_bio_hr_self_parsed %>%
#   subset(screencontent_no>2)%>%
#   group_by(ssid)%>%
#   summarise_if(is.numeric,mean, na.rm = TRUE)%>%
#   ggplot(aes(Age,sdev_gazesum))+
#   geom_point()+
#   geom_smooth(method = lm, se = F)

colnames(tmp.df4_sum_full_bio_hr_self_parsed)

tmp.df4_sum_full_bio_hr_self_parsed$Age<- tmp.df4_sum_full_bio_hr_self_parsed$age_response_specific
tmp.df4_sum_full_bio_hr_self_parsed$gender<- substr(tmp.df4_sum_full_bio_hr_self_parsed$gender_response,1,1)

tmp.df4_sum_full_bio_hr_self_parsed$BIO_filename<- NULL
tmp.df4_sum_full_bio_hr_self_parsed$`Participant Completion Code`<- NULL
tmp.df4_sum_full_bio_hr_self_parsed$`Participant Private ID`<- NULL

tmp.df4_sum_full_bio_hr_self_parsed$`Participant No`<- NULL
tmp.df4_sum_full_bio_hr_self_parsed$age_response_specific<- NULL
tmp.df4_sum_full_bio_hr_self_parsed$Event.NID<- NULL
tmp.df4_sum_full_bio_hr_self_parsed$`Event Index`<- NULL
tmp.df4_sum_full_bio_hr_self_parsed$gender_response<- NULL

tmp.df4_sum_full_bio_hr_self_parsed$`Person testing`<- NULL
tmp.df4_sum_full_bio_hr_self_parsed$Event.Nr.x<- NULL
tmp.df4_sum_full_bio_hr_self_parsed$filename.x<- NULL
tmp.df4_sum_full_bio_hr_self_parsed$filename.y<- NULL

tmp.df4_sum_full_bio_hr_self_parsed

tmp.df4_sum_full_bio_hr_self_parsed<- tmp.df4_sum_full_bio_hr_self_parsed%>%
  rename(IAS = IAS_score)%>%
  rename(ASD_self = ASD)

# tmp.df4_sum_full_bio_hr_self_parsed1<- select(tmp.df4_sum_full_bio_hr_self_parsed,)

write_csv(tmp.df4_sum_full_bio_hr_self_parsed, 'tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv')
write_csv(tmp.df4, 'tmp.df4_timeseries_345_356.csv')
```

>>>>

tmp.df4$trigger2<- tmp.df4$trigger

@@

unique(tmp.df4$trigger2)

# \why?
tmp.df4<- tmp.df4%>%
  group_by(ssid, tNo, text)%>%
  mutate(stdev_gaze_x = sd(gaze_x_cor_pix, na.rm = TRUE))%>%
  mutate(stdev_gaze_y = sd(gaze_y_cor_pix, na.rm = TRUE))

@@

db_parsed$screencontent_no<- if_else(db_parsed$screencontent == 'fixation', 1,
                                      if_else(db_parsed$screencontent == 'stim', 2,
                                              if_else(db_parsed$screencontent == 'ValenceResp', 3,
                                                      if_else(db_parsed$screencontent == 'IntResp', 4, NULL))))

@@

# rm(tmp.df4_sum_fullt)
# testna<- subset(tmp.df4_sum_fullt, is.na(tmp.df4_sum_fullt$mean_fix_dur) == TRUE)
# 
# tmp.df4_sum_fullt
```

@@

db_beh2$triggeracq<- db_beh2$trigger
unique(db_beh2$ssid)

@@

# tmp.df4_sum_full<- tmp.df4_sum_full%>%
#   arrange(ssid, tNo, screencontent_no)
```

@@

View(tmp.df4_sum_full)
```

@@

db_leda_bio$trigger<- as.numeric(db_leda_bio$BIO_Event.NID)

@@

unique(db_leda_bio$trigger)

db_leda_bio_stim<-subset(db_leda_bio, db_leda_bio$trigger< 100)
unique(db_leda_bio_stim$trigger)

@@

#tmp.df4_sum_full_bio<- subset(tmp.df4_sum_full, tmp.df4_sum_full$ssid>303)
# tmp.df4_sum_full_bio<- subset(tmp.df4_sum_full_bio, tmp.df4_sum_full_bio$trigger!= -7)

#levels(as.factor(tmp.df4_sum_full_bio$ssid))
#unique(tmp.df4_sum_full_bio$trigger)
#levels(as.factor(db_leda_bio$ssid))

@@

db_leda_bio_stim$trigger<- as.character(db_leda_bio_stim$trigger)

#db_leda_bio$order<- db_leda_bio$Event.Nr
tmp.df4_sum_full_stim_gp_leda_beh_self$ssid<- as.character(tmp.df4_sum_full_stim_gp_leda_beh_self$ssid)
tmp.df4_sum_full_stim_gp_leda_beh_self$trigger<- as.character(tmp.df4_sum_full_stim_gp_leda_beh_self$trigger)

@@

cor(tmp.df4_sum_full_biot1$arousal, tmp.df4_sum_full_biot1$Global.Mean.y, use = 'complete.obs')
```

import biopac heart rate
```{r}
nrow(tmp.df4_sum_full_bio)

# now read them
db_biohr <-
  list.files(pattern = "*.csv", 
             full.names = T) %>% 
  map_df(~read_biohr(.))

db_biohr$Order<- NULL
db_biohr$filename<- NULL
db_biohr$trigger<- as.factor(as.character(db_biohr$trigger))
unique(tmp.df4_sum_full_bio$ssid)
unique(db_biohr$ssid)
tmp.df4_sum_full_bio$trigger<- as.factor(as.character(tmp.df4_sum_full_bio$trigger))

db_biohr$ssid<- as.factor(as.character(db_biohr$ssid))
tmp.df4_sum_full_bio_hr<- left_join(tmp.df4_sum_full_biot, db_biohr, by = c('ssid', 'order', 'trigger'))

ggplot(subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent == 'stim'), aes(hr, HR_BIO))+
  geom_point()+
  geom_smooth(method = 'lm')

ggplot(subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent == 'stim'), aes(CDA.PhasicMax.x, CDA.PhasicMax.y))+
  geom_point()+
  geom_smooth(method = 'lm')
tmp.df4_sum_full_bio_hr_stim<- subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent != 'fixation')

cor(tmp.df4_sum_full_bio_hr_stim$hr, tmp.df4_sum_full_bio_hr_stim$HR_BIO, use = 'complete')

# tmp.df4_sum_full_bio_hr_stim_1<- subset(tmp.df4_sum_full_bio_hr_stim, tmp.df4_sum_full_bio_hr_stim$HR_BIO> 50)

tmp.df4_sum_full_bio_hr_stim$valence_cat<- if_else(tmp.df4_sum_full_bio_hr_stim$valence >0, 'pos',
                                                  if_else(tmp.df4_sum_full_bio_hr_stim$valence < 0, 'neg', 'neutral'))

unique(tmp.df4_sum_full_bio_hr_stim$screencontent)

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, arousal))+
  geom_point()+
  geom_smooth(method = 'lm')
  # facet_grid(~valence_cat)

cor(tmp.df4_sum_full_bio_hr_stim$HR_BIO, tmp.df4_sum_full_bio_hr_stim$arousal, use = 'complete')
cor(tmp.df4_sum_full_bio_hr_stim$HR_BIO, tmp.df4_sum_full_bio_hr_stim$valence, use = 'complete')

tmp.df4_sum_full_bio_hr_stim%>%
      group_by(ssid, IAS)%>%
      summarise(corr = cor(HR_BIO, arousal, use = 'complete'))%>%
  summarise(new = cor(corr, IAS))
  # summarise_at(c('TAS'), mean)

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, arousal))+
  geom_point()+
  geom_smooth(method = 'lm')+
  facet_grid(~valence_cat)

tmp.df4_sum_full_bio_hr_stim%>%
group_by(valence_cat)%>%
  summarise(corr = cor(HR_BIO, arousal, use = 'complete'))
ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, valence))+
  geom_point()+
  geom_smooth(method = 'lm')+
  facet_grid(~valence_cat)

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, ValenceMean))+
  geom_point()+
  geom_smooth(method = 'lm')
  # facet_grid(~valence_cat)

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, mean_sac_dur))+
  geom_point()+
  geom_smooth(method = 'lm')+
  facet_grid(~valence_cat)

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, pup_basCor))+
  geom_point()+
  geom_smooth(method = 'lm')+
  facet_grid(~valence_cat)

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, Global.Mean.y))+
  geom_point()+
  geom_smooth(method = 'lm')

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, TAS))+
  geom_point()+
  geom_smooth(method = 'lm')

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, `DASS Anxiety`))+
  geom_point()+
  geom_smooth(method = 'lm')

@@
